Flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-05-17 src/tex/ms.tex
[showyourwork] overleaf sync

@@

\subsection{K2-354}
We note that we found K2-354 under EPIC 211314705 and K2-329(!) in \cite{bouma2020cluster}, who refer to the detection paper \cite{pope2016transiting}, and also under TIC 468989066.
\end{document}

>>>>

We compared our derived values for $Ro$ and $B$ with existing estimates of coronal emission from~\citet{foster2022exoplanet}. We show $L_X/L_{\rm bol}$ as a function of $Ro$ and $B$ in Fig.~\ref{fig:lx}. The X-ray emission relation to Rossby number in our sample follows that of stars that are not known to host close-in planets~\citep{wright2011stellaractivityrotation}, spanning both the saturated and unsaturated regime. The X-ray emission and our estimated magnetic field closely follow each other, also consistent with stars without known close-in planets~(XXXX). There are two exceptions: GJ 3082 appears underluminous in X-ray compared to its Rossby number and expected magnetic field strength. AU Mic is slightly overluminous, falling somewhat above the saturated level of $L_X/L_{\rm bol}$. However, the star still follows the $B-L_X/L_{\rm bol}$ relation.

\begin{figure}[ht!]
    \script{paper_lxl_plots.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_lxlbol.png}
        \caption{
           X-ray luminosity over bolometric luminosity compared to Rossby number (\textbf{upper panel}), and surface magnetic field strength (\textbf{lower panel}). Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3323, which is underluminous for its Rossby number, and hence also its estimated magnetic field strength.
        }
        \label{fig:coherence_hist}
    \end{centering}
\end{figure}

@@

\subsection{K2-354}
We note that we found K2-354 under EPIC 211314705 and K2-329(!) in \cite{bouma2020cluster}, who refer to the detection paper \cite{pope2016transiting}, and also under TIC 468989066.

\section{Expected power vs. AD test, colorcoded by Rossby number}
\begin{figure*}[ht!]
    \script{paper_adtest_vs_value_scatterplots.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_bg.png}
        \caption{
        Expected power of SPI vs. AD test results, assuming the same four different scenarios as in Fig.~\ref{fig:adtest_bp}, color-coded by Rossby number. $R\rm o=0.3$ is chosen to mark the transition from the saturated ($R\rm o < 0.3$) to the unsaturated ($R\rm o > 0.3$) activity regime. 
        }
        \label{fig:adtest_bp}
    \end{centering}
\end{figure*}

\end{document}
